How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-04-16 tse-paper/content.tex
corrections big study dicussion

The first section discusses for PBE, CTS and KWS separately in which
cases they perform best.
It details for which types of input build
logs, available training examples and consumption of the retrieved
output each technique is suited.
In the following section we discuss
which of these criteria should influence the decision to use a certain
technique most.
Based on our empirical comparison, we present a
decision tree between the three techniques we investigated.

\subsection{Interpretation of Study Results}
This section discusses the study results for each of the analyzed
chunk retrieval techniques separately.
It gives recommendations which
kind of information chunk targets are best for each technique and for
what kind of usage the respective output is suitable.

@@

\noindent
\textbf{Configuration and Input}
Our study results show that chunk retrieval with PBE gives best
results when the training examples are structurally identical.
This is
because PROSE has difficulty synthesizing OR-based programs (see
\Cref{sec:prose:impl}).
PBE is thus suited to retrieve information
chunks that always have the same surrounding or defining internal
structure.
To extract for example the reason a build failed, the log
passage describing the failure would always have to be started and
ended the same way.

When the training examples are of the same structure, even one or two
two examples are enough input for PROSE to synthesize a regular
expression program with good recall.
In our study, additional training
examples did not improve the chunk retrieval.
In fact, unless they
were in some sense redudant, adding training examples above that even
hindered the applicability of PBE.

\noindent
\textbf{Retrieval Output Usage}
If the program synthesis succeeds and applying the regular expression
program yields an output, PBE has high precision and recall.
The tool
clearly identifies a failing program synthesis or when no output from
the program applied to a build log is obtained.
Therefore, if there is
an output, the user can have high confidence that it is the desired
output.
This preciseness makes output from PBE chunk retrieval
well-suited for machine consumption.

@@

Going from one to two two training examples, KWS's recall improves
siginficantly.
However, further enlarging the training example count
does not lead to further improvments.

Retrieving the average number of lines present in the outputs of the
training examples around every found keyword yields reasonable recall.
Selecting 1.5 times as many lines around every found keyword does
improve the recall within our study but also increases the proportion
of lines retrieved overall and therefore decreases precision.

@@

\subsection{Recommendation of Suitable Techniques}
After discussing the three chunk retrieval techniques separately we
now want to unify our results into one recommendation scheme.
In
Figure~\ref{fig:crt-recommendation}, we present a decision tree, which
developers and researchers who want to retrieve information chunks
from build logs can follow.
The decision tree is built up of questions
which either lead to more questions or to a leaf node containing a
recommended technique.

\noindent
\textbf{Caveat!} This is a preliminary hypothesis based on the results
from our comparison study.
The recommendations could therefore be
influenced by idiosyncrazies of our specific implementation of the
chunk retrieval techniques as well as the logs in the \emph{LogChunks}
data set.

This decision tree in \Cref{fig:crt-recommendation} gives a nunanced
answer to RQ2, about which criteria influence the suitability of a
chunk retrieval technique.
The earlier in the decision tree a
criterion is noted, the more important it is when distinguishing the
techniques.

The first and most important aspect are the structural categories.
Are
the information chunks one would like to retrieve always presented in
the same structural way within the build logs? Then the information
chunks in all training examples and the analyzed build log are in the
same structural category.

If the information chunks are from multiple structural categories,
i.e.\ they are not represented in the same structural way within the
build logs, and recall is more important than precision we recommend
to use KWS\@.
If the representations are from multiple structural
categories and precision is more important than recall to the user we
recommend CTS\@.
We also recommend CTS when the representations are
from one structural category, when the user does not require a high
confidence in the precision or recall of the outcome and when the user
would rather have output with low recall instead of no output at all.
When the representations are from one structural category and the user
wishes a high confidence in the correctness of the output or prefers
no output over output with low recall, we recommend PBE\@.

@@

\noindent
\textbf{Example of Using the Recommendation Scheme}
To illustrate how one would use our decision tree to find a suitable
chunk retrieval technique we describe two concrete examples: a
researcher investigating why CI builds fail and a software team
wanting to monitor their build performance.

In our first example, a researcher studies whether test failures in CI
are caused by a small or by a large group of test cases.
They gather
CI build logs from various projects, which are their only available
data source.
The task of the researcher is to extract the names of the
failing test cases from each build log.
When they use our
recommendation scheme to select a chunk retrieval technique, they
first have to estimate how uniform the representation of the failing
test cases is in the investigated build logs.
As the researcher is
covering a wide range of build tools and development languages, the
log chunks they target are in various, non-predictable structural
representations.
The next question is whether they value precision
over recall.
As they have to manually inspect the results of both CTS
and KWS, they choose recall over precision to avoid having to inspect
the whole log in case the relevant information chunk was not
retrieved.
Therefore, our decision tree recommends them to use KWS\@.

@@

In our second example, a software development team wants to monitor
the performance of the phases within their CI build.
They are using
Travis CI, which measures the duration of build phases and documents
them within the build log.
As all log statements that report timing
measurements are formatted the same way, the targeted log chunks are
from one structural category.
Therefore the development team can use
PBE to retrieve the duration of a build phase as well as its name.

@@

There are various future research opportunities based on our work:
\begin{itemize}
  \item \textbf{Systematic Survey of Industry Approaches for Build
  Log Analysis} Our survey is limited to academic work and articles.
  However, handling build logs is a challenge for a wide range of
  practitioners as well.
  We propose to investigate the methods used in industry to analyze
  build logs.
  An example is the Jenkins \emph{build-failure-analyzer}
  plugin~\cite{jenkins2020failure-analyzer} or automatically
  inferred test results in Azure~\cite{azure2020inferred}.
  \item \textbf{Further Analysis of \emph{LogChunks}} We created the
  \emph{LogChunks} data set \cite{brandt2020logchunks} specifically for
  the comparative
  study in this paper, though it can be the basis for various further
  analyses of build log data.
  The keywords, for example, can be
  investigated to answer which keywords are used to search for the
  reason the build failed within build logs.
  \item \textbf{Cross-Repository Build Log Analysis} We trained and
  tested each chunk retrieval technique on examples from the same
  repository.
  We propose to analyze how techniques could be trained
  across repositories, building the cornerstones for build
  environment-agnostic analysis tools.
  \item \textbf{Comparison with more Chunk Retrieval Techniques} This
  paper investigates the three chunk retrieval techniques PBE, CTS and
  KWS\@.
  Our study design can be reused to evaluate other build log
  analysis techniques, such as the diff and information retrieval
  approach by Amar et al.~\cite{amar2019mining}.
  \item \textbf{Refinement of Retrieval Quality for each Technique} We
  investigated basic configurations of existing techniques applied to
  chunk retrieval from build logs.
  In a next step, each of these
  techniques could be refined to better approach the domain of build
  logs.
  The \emph{LogChunks} data set and our study results act as a
  baseline to benchmark such technique improvements.
  We propose the
  following improvements:
    \begin{itemize}
      \item \textbf{Custom Ranking and Tokens for PBE} The program
      synthesis through PROSE ranks possible programs according to
      what the user most likely intended.
      One could adapt the ranking
      rules provided by the FlashExtract DSL to fit common build log
      chunk retrieval tasks.
      FlashExtract includes special tokens when
      enumerating possible regular expressions.
      One could extend these
      with tokens found in build logs, such as ``-'',``='',``ERROR''
      or ``[OK''.
      \item \textbf{Meta-Parameter Optimization for CTS} Information
      retrieval techniques have various meta-parameters which can be
      optimized for the specific use
      case~\cite{panichella2016parameterizing}.
      We propose to further
      investigate improvements in preprocessing of the log text, in
      tokenization of the log lines into terms and in stop words
      lists.
    \end{itemize}
  \item \textbf{Usability Analysis of Chunk Retrieval Output} Our
  analysis of the output produced by the chunk retrieval focuses on
  precision and recall.
  The next step would be to investigate how useful these
  outputs are to developers through controlled experiments.
\end{itemize}

>>>>

For the interpretation of our study results we look at each chunk
retrieval technique separately and give recommendations for
which types of input build
logs, available training examples and consumption of the retrieved
output each technique is suited.
Following that, we discuss
which of these criteria should influence the decision to use a certain
chunk retrieval technique most.
Based on our empirical comparison, we present a
decision tree between the three techniques we investigated.

\subsection{Interpretation of Study Results}
\Cref{tab:single-technique-recommendations} summarizes the
recommendations which we discuss
in this section.

@@

\noindent
\textbf{Configuration and Input}
Our study results show that chunk retrieval with PBE gives best
results when the training examples are structurally identical.
This is
because PROSE has difficulty synthesizing OR-based
programs~\cite{mayer2015user}.
PBE is thus suited to retrieve information
chunks that always have the same defining surrounding or internal
structure.
To extract for example the reason a build failed, the log
passage describing the failure would always have to be started and
ended the same way.

When the training examples are of the same structure, one or two
two examples are enough input for PROSE to synthesize a regular
expression program with good recall.
In our study, additional training
examples did not improve the chunk retrieval.
% In fact, unless they
% were in some sense redudant, adding training examples above that even
% hindered the applicability of PBE.

\noindent
\textbf{Retrieval Output Usage}
If the program synthesis succeeds and applying the regular expression
program yields an output, PBE has high precision and recall.
The tool
clearly identifies a failing synthesis or when the regular expression
finds no match on a build log.
Therefore, if PBE produces
an output, the user can have high confidence that it is the desired
output.
This preciseness makes output from PBE chunk retrieval
well-suited for machine consumption and therefore automatic on-ward
processing.

@@

Going from one to two training examples, KWS's recall improves
significantly.
However, further enlarging the training set
does not lead to further improvements.

@@

\subsection{Recommendation of Suitable Techniques}
After discussing the three chunk retrieval techniques separately we
now want to unify our results into one recommendation scheme.
Figure~\ref{fig:crt-recommendation} presents a decision tree
to answer our second research question;
If researchers or developers want to retrieve chunks from build logs,
they can follow the decision tree to identify the technique
suited best for their use case.
The decision tree is built up of questions
which either lead to more questions or to a leaf node containing a
recommended technique.

\begin{simplebox}[minipage boxed title*=-7cm]{Caveat!}
This is a preliminary hypothesis based on the results
from our comparison study.
The recommendations could therefore be
influenced by idiosyncrazies of our specific implementation of the
chunk retrieval techniques as well as the \emph{LogChunks}
data set.
\end{simplebox}

The first and most important aspect are the structural categories.
Are the targeted log chunks always presented in
the same structural way within the build logs? Then the information
chunks in all training examples and the analyzed build log are in the
same structural category.

If the information chunks are from multiple structural categories
and recall is more important than precision we recommend
to use KWS\@.
If precision is more important than recall to the user we
recommend CTS\@.
We also recommend CTS when the log chunks are
from one structural category, when the user does not require a high
confidence in the precision or recall of the outcome and when one
would rather have output with low recall instead of no output at all.
When the representations are from one structural category and the user
wishes a high confidence in the correctness of the output or prefers
no output over output with low recall, we recommend PBE\@.

@@

\subsection{Examples of Using the Recommendation Scheme}
To illustrate how one would use our decision tree to find a suitable
chunk retrieval technique we describe two concrete examples: a software
team
wanting to monitor their build performance and a
researcher investigating why builds fail.

In our first example, a software development team wants to monitor
the performance of the phases within their CI build.
They are using
Travis CI, which measures the duration of build phases and documents
this within the build log.
As all log statements that report timing
measurements are formatted the same way, the targeted log chunks are
from one structural category.
Therefore the development team can use
PBE to retrieve the duration of a build phase.

In our second example, a researcher studies whether test failures
are caused by a small or by a large group of test cases.
They gather
CI build logs from various projects, which are their only available
data source.
The task of the researcher is to extract the names of the
failing test cases from each build log.
When they use our
recommendation scheme to select a chunk retrieval technique, they
first have to estimate how uniform the representation of the failing
test cases is in the investigated build logs.
As the researcher is
covering a wide range of test tools, the
log chunks they target are in various, non-predictable structural
representations.
The next question is whether they value precision
over recall.
As they have to manually inspect the results of both CTS
and KWS, they choose recall over precision to avoid having to inspect
the whole log in case the relevant information chunk was not
retrieved.
Therefore, our decision tree recommends to the researcher to use KWS\@.

@@

@@

There are various future research opportunities based on our work:

\textbf{Systematic Survey of Industry Approaches for Build
Log Analysis}
Our survey is limited to academic work and articles.
However, handling build logs is a challenge for a wide range of
practitioners as well.
We propose to investigate the methods used in industry to analyze
build logs.
An example is the Jenkins \emph{build-failure-analyzer}
plugin~\cite{jenkins2020failure-analyzer} or automatically
inferred test results in Azure~\cite{azure2020inferred}.

\textbf{Further Analysis of \emph{LogChunks}}
We created the
\emph{LogChunks} data set \cite{brandt2020logchunks} specifically for
the comparative
study in this paper, though it can be the basis for various further
analyses of build log data.
The keywords, for example, can be
investigated to answer which keywords are used to search for the
reason the build failed within build logs.

\textbf{Cross-Repository Build Log Analysis}
We trained and
tested each chunk retrieval technique on examples from the same
repository.
We propose to analyze how techniques could be trained
across repositories, building the cornerstones for build
environment-agnostic analysis tools.

\textbf{Comparison with more Chunk Retrieval Techniques}
This
paper investigates the three chunk retrieval techniques PBE, CTS and
KWS\@.
Our study design can be reused to evaluate other build log
analysis techniques, such as the diff and information retrieval
approach by Amar et al.~\cite{amar2019mining}.

\textbf{Refinement of Retrieval Quality for each Technique} We
investigated basic configurations of existing techniques applied to
chunk retrieval from build logs.
In a next step, each of these
techniques could be refined to better approach the domain of build
logs.
The \emph{LogChunks} data set and our study results act as a
baseline to benchmark such technique improvements.
We propose the
following improvements:
\begin{itemize}
  \item \textbf{Custom Ranking and Tokens for PBE} The program
  synthesis through PROSE ranks possible programs according to
  what the user most likely intended.
  One could adapt the ranking
  rules provided by the FlashExtract DSL to fit common build log
  chunk retrieval tasks.
  FlashExtract includes special tokens when
  enumerating possible regular expressions.
  One could extend these
  with tokens found in build logs, such as ``-'',``='',``ERROR''
  or ``[OK''.
  \item \textbf{Meta-Parameter Optimization for CTS} Information
  retrieval techniques have various meta-parameters which can be
  optimized for the specific use
  case~\cite{panichella2016parameterizing}.
  We propose to further
  investigate improvements in preprocessing of the log text, in
  tokenization of the log lines into terms and in stop words
  lists.
\end{itemize}

\textbf{Usability Analysis of Chunk Retrieval Output}
Our
analysis of the output produced by the chunk retrieval focuses on
precision and recall.
The next step would be to investigate how useful these
outputs are to developers through controlled experiments.
